\chapter*{Acknowledgements}

First, I would like to thank my promoters for giving me the opportunity to do my master thesis on such an interesting topic, and for sharing their knowledge and experience with me. I have learned more from this work than I have from any other courses that I have followed during my cursus (except \textit{Physique Générale} maybe...). I am grateful to Marc Haelterman for considering me as legitimate PhD candidate and for showing me what were the humane qualities that make a good scientist. I would also like to thank Serge Massar for his advice, his reactivity to answer my questions and for the last minute review of the thesis that he did. Many thanks to Lorenz Butschek without whom this thesis would not exist. Thank you for all the time you spent with me in the lab, for your patience when you were explaining (sometimes very basic) things, for the very careful rereading of the thesis that you did in last minute, and for your ability to decode my English which can get sometimes quite approximative. Once again, a big thank you for all of this. Before leaving the academics to move on to more personal acknowledgments, I would like to thank Michel Kinnaert who accepted to meet me twice throughout the year and with whom I passionately discussed the stabilisation issues encountered. I would finally like to thank my readers for the time they will invest in my work. I hope you will enjoy it. It is now time to thank my closest ones. First, I would like to thank my parents for giving me the opportunity to pursue higher education. Going to university is a privilege that is too often forgotten, and I am thankful they offered me this chance. Finally, I want to thank by biggest support of all, Cassandra. During this year, she shared my ups, and helped me during the downs, she always knew how the cheer me up when the work was not progressing the way I wanted. Thank you for being the amazing person that you are.